---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# finanzR

<!-- badges: start -->
<!-- badges: end -->

finanzR was developed as a personal library of scripts to facilitate financial tracking in [Portfolio Performance](https://www.portfolio-performance.info/).

Since these may also help others, I have decided to publish the library.

At the moment the package is in an early beta and testing phase, but will be extended in the future.

If you have any suggestions or find any bugs, feel free to create a new issue. Since this is my first R package, it is possible that there will be changes in the architecture during the development.

## Installation

You can install the development version of finanzR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jak3sch/finanzR")
```

## Usage

For more detailed information, please refer to the [documentation](https://jak3sch.github.io/finanzR/).

### Crypto Staking (Kraken)

`{finanzR}` tries to solve the problem that staking cannot really be mapped in Portfolio Performance. Currently the function only supports staking at [Kraken](https://www.kraken.com/).

```{r example}
library(finanzR)

# kraken ledgers export
kraken_data <- data.frame(
  time = c("2022-04-05 03:24:26", "2022-04-11 17:51:44", "2022-04-12 02:43:49", 
           "2022-04-18 09:07:51", "2022-04-19 02:46:48", "2022-04-25 09:11:56", 
           "2022-04-26 02:48:12"), 
  type = "staking",
  asset = c("TRX.S", "ADA.S", "TRX.S", "ADA.S", "TRX.S", "ADA.S", "TRX.S"),
  amount = c(0.4, 0.55, 10.76, 0.55, 10.77, 0.55, 10.79)
)

staking_data <- finanzR::kraken_staking(input = kraken_data, input_type = "data.frame")

print(staking_data)
```

The function takes the exported ledger data from Kraken. It searches the CoinGecko api for the price of the coin on the day of the staking transaction.

It then creates 2 transactions each for Portfolio Performance: a dividend and a purchase.

Since we only have the day's price, it's not 100% accurate, but it's better than nothing.